---
title: "R-markdown-workshop"
author: "Carina Fan for psychhacks2019"
date: "`r format(Sys.time(), '%B, %d, %Y')`"
output: 
  html_document:
  toc: true
editor_options: 
  chunk_output_type: console
---
R markdown is a regular text document with chunks of code (R) embedded within.

The text document can be written in markdown (.Rmd) or in LaTex (.Rnw)

When file is compiled a new environment R is made, and the code chunks are run
so if you're running big data it might take while to compile.

markdown -> plain R file, use purl()

additional resources: http://tinyurl.com/rmarkdown-resources
  
  ```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE) # warnings = False, messages = False
#knitr::opts_knit$set(root.dir = "~/Desktop") # reference diff directory set this way
# global options
```

# Set up 
## loading packages

```{r}
# ctrl+alt+i -> to add an r block
# install.packages("knitr")

library(tidyverse)
library(knitr)
```

## loading data

```{r}
data(sleep) # shows as <Promise>, turn into df by calling sleep 
sleep
# cmd + shift + k -> to knit 
```

# Analyze data 

```{r}
ttest = t.test(extra~group, paired = TRUE, data = sleep)

```
Yes, there is a difference between the drugs: t(`r ttest$parameter`)= `r  ttest$statistic %>% round(2)`, p = `r ttest$p.value %>% round(3)`.

```{r}
sleep %>%
  ggplot(aes(x = group, y= extra, colour = group, fill= group)) +
  geom_violin(alpha = .2) + 
  geom_point(alpha = .8, position = "jitter") + 
  stat_summary(fun.y = mean,
               geom = "point", 
               size = 4, 
               colour = "black") + 
  stat_summary(fun.data = mean_cl_boot, geom = "errorbar", width = .1, colour = "black") + 
  theme_bw() + 
  labs(x = "drug", 
       y = "number of extra hours of sleep", 
       title = "Effects of drugs on sleep") +
  guides(colour = FALSE, fill = FALSE) + 
  scale_colour_manual(values=c("darkcyan", "darkorchid3")) + 
  scale_fill_manual(values=c("darkcyan", "darkorchid3")) 

```
```{r}
ggsave("drugs.png", dpi = 300, width = 6, height = 6, unit = "in")
# need bookdown, to make references for figures and things
# html document, fig captions
# see figure \ref{fig:plot} name block chunk and reference it for results 
```